---
title: "Game Sales Analysis"
author: "Alexander King"
date: "March 21, 2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#CSV of Video Game Sales
Importing Video Game Sales
```{r echo=FALSE}
  dataset <- as.data.frame(read.csv("C:\\Users\\laifu\\Desktop\\CIS 585 Video Game Sales Analysis\\Video_Games_Sales_as_at_22_Dec_2016.csv"))
  sales = subset(dataset, select= -c(Year_of_Release, Publisher, NA_Sales, EU_Sales, JP_Sales, Other_Sales, Developer, Rating))
  print(sales)
  
```

#Reddit API Data
Retrieving Data from Reddit's API
```{r echo=FALSE}
  

```

#Twitch API Data
Retrieving Data from Twitch TV's API
```{r echo=FALSE}
  require(jsonlite)
  require(dplyr)
  require(plyr)
  require(rTwitchAPI)
  twitch_auth("3s4qog8agruu7dz6gquv0nsk2mg7fd")
  get_top_games()
  i <- 1
  #Only GTA V at the moment for testing purposes
  while(hasNext(get_streams(game_id="32982"))){
    gamestreams <- get_streams(game_id="32982")
    print(count(gamestreams[i:i+20], vars="id"))
    i <- i+1
  }
  gamestreams <- get_streams(game_id="32982")
  print(count(gamestreams))
```

#Giant Bomb API Data
Retrieving Data from Giant Bomb's API
```{r echo=FALSE}
  require(giantbomb)
  Sys.setenv("GB_KEY" = "535c08b192ce6572613e8db5cdc612d3e366a88f")
  gb_games(
    n = 10,
    filter= "name:grand theft auto",
    sort = "date_added:desc",
    field_list = c("date_added", "name", "id")
    )
  #only GTA at the moment for testing purposes
  review <- gb_reviews(
    n = 1,
    filter= "game:36765",
    field_list = c("score", "id","game")
  )
  print(review)

```

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



